---
title: "Cleaning for Nursing Pilot Oct 2016 data"
author: "Kate Block"
date: "`r format(Sys.Date())`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, message=FALSE}
library (tidyverse)
library (ggplot2)
library(knitr)
```

# 0.1) renaming variables so they make sense and making composite variables

* First, I read in the data
```{r, message=FALSE}
rawdata <- read_csv ("/Users/KatharinaBlock/Desktop/Git_REPOS/NursingDVPilot_oct2016/Nursing2pilot.csv")

str (rawdata)
```

* Then I ranmed the variables so they make more intuitive sense, having things named V2 does not make sense

```{r}
raw_renamed <- rawdata %>% rename(ID= V1, start= V8, Ra_ID=Q2,
                   end= V9, log= Q93,
                   helping = Q77_1, status=Q77_2, working_people=Q77_3,
                   achievement=Q77_4, attenting= Q77_5, self_promo= Q77_6, connection=Q77_7,
                   power=Q77_8, intimacy= Q77_9, caring=Q77_10,
                   independence=Q77_11, serving_humanity=Q77_12, competition=Q77_13,
                   recognition=Q77_14, rate_men_nursing=Q75,male_nurse_positive=Q77,
                   interest_nursing=Q76, enjoy_nursing=Q74, imagine_nursing=Q70, 
                   rank_lawclerk= Q78_1, rank_ITassistant=Q78_2, rank_softwareENG=Q78_3,
                   rank_nurse=Q78_4,rank_teacher=Q78_5,rank_immigrationofficer=Q78_6,
                   rank_businessanalyst=Q78_7, rank_accountant=Q78_8,rank_insurance_agent=Q78_9,
                   rank_counselor=Q78_10, rank_pharmacist=Q78_11, rank_graphicdesigner=Q78_12,
                   rank_HRmanager=Q78_13,rank_copywriter=Q78_14,rank_curator=Q78_15,
                   fit1=Q96_4,fit2=Q96_8, fit3=Q96_9,fit4=Q96_10, fit5=Q96_11,fit6=Q96_12,
                   nursing_overlap=Q102, gender=Q17,
                   when_learn_english=Q11,year_standing=Q13,
                   ethnicity=Q15,ethnicity_other=Q15_TEXT,faculty=Q19,
                   major=Q84,sexual_orientation=Q85,sexual_other=Q85_TEXT,
                   what_about=Q18)
                   
# Drop Q80, Q95, Q94, =Q98, Q101, which are not really variables at all
raw_renamed <- raw_renamed %>% select(-Q80, -Q95, -Q94, -Q98, -Q101)
  
```

*then i make composite variables

```{r}
raw_renamed <- 
  raw_renamed %>% 
  mutate(communal_values= (helping+working_people+attenting+connection+caring+serving_humanity)/6,
         agentic_values= (status+achievement+self_promo+power+intimacy+independence+competition+recognition)/7, fit_nursing= (fit1+fit2+fit3+fit4+fit5+fit6)/6, interest_comp = (interest_nursing+enjoy_nursing+imagine_nursing)/3)

```

* Dropping some more variables: I drop the individual communal and agentic values here bc we can be quite confident in those, as we have previously used them.

```{r}
CLEANdata <- raw_renamed %>% select (-V10, -start, -helping, -working_people, -attenting, -connection, -caring,-serving_humanity, - status, -achievement, -self_promo, -power, -intimacy, -independence, -competition, -recognition)

# looks better now
str (CLEANdata)
```

# 0.2) Revaluing ethnicity to get bigger groups.
* I choose to revalue my ethinicity factor here, I have to many groups,

```{r}
# so here you can see there is a lot of ethnicity groups
CLEANdata %>% select (ethnicity) %>% 
                      group_by(ethnicity) %>% summarize(particicipants=n()) %>% kable

CLEANdata$ethcode <- plyr::revalue(CLEANdata$ethnicity, c("East Asian or Pacific Islander"="Asian","South Asian (e.g. India)"="Asian", "White/Caucasian"="White", "Black/African American/Canadian"="Other", "Hispanic/Latino"="Other","Middle Eastern"="Other","More than one"="Other","Native Canadian/Aboriginal/Native American"="Other", "Other (please specify)"="Other"))

CLEANdata %>% 
  group_by(ethcode) %>% select (ethnicity) %>% 
  summarize(particicipants=n()) %>% kable
```

# 1) Exclusions

I decided to drop those who identify as **anything other than heterosexual** and* **didn't identify as male or female**
    
```{r}
#make this a factor instead of a character
CLEANdata$sexual_orientation <- as.factor(CLEANdata$sexual_orientation)

str(CLEANdata$sexual_orientation)

CLEAN_hetero <- CLEANdata %>% 
  filter(sexual_orientation != "Mostly Homosexual/Gay/Lesbian" & 
           sexual_orientation != "Bisexual" & gender != "Neither reflects my gender identity")

# this dropped a total of 31 participants!
```

# 2) Write Clean data

I then write the clean data to file so I can use that one for my next script

```{r}
write_csv(CLEAN_hetero,"/Users/KatharinaBlock/Desktop/Git_REPOS/NursingDVPilot_oct2016/Nursing2pilot_clean_hetero.csv")
```

